### 2019-05-28 Scrap/manuscript.rmd
cleaned up repo

>>>>

##SIMMAP feeding guilds ##
make.simmap(regimetree, hypdiet, nsim = 100) -> feeding_sim
plotTree(regimetree, lwd = 4)
feeding_sim %>% plotSimmap(lwd = 4, add = T)
colors = c( "black","green3","blue","cyan","red")
names(colors) = c("Fish","Large crustacean","Mixed","Small crustacean","Gelatinous")
nodelabels(pie=(describe.simmap(feeding_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)

### 2019-05-28 manuscript_clean.Rmd
cleaned up repo

^1^ Osborn Memorial Laboratories, Department of Ecology and Evolutionary Biology, 165 Prospect St., Yale University, New Haven, CT 06520, USA

@@

*Tentilla morphology* – The morphological work was carried out on siphonophore specimens fixed in 4% formalin from the Yale Peabody Museum Invertebrate Zoology (YPM-IZ) collection (catalog numbers in Appendix 1). These specimens had been collected intact across many years of fieldwork expeditions, by the means of blue-water Diving [@haddock2005scientific], remotely operated vehicles (ROVs), and human-operated submersibles. Tentacles were dissected from non-larval gastrozooids, sequentially dehydrated into 100% ethanol, cleared in methyl salicylate, and mounted into slides with Canada Balsam or Permount mounting media. The slides were imaged as tiled z-stacks using differential interference contrast (DIC) on an automated stage at YPM-IZ (with the assistance of Daniel Drew and Eric Lazo-Wasem) and laser point confocal microscopy using a 488 nm Argon laser that excited autofluorescence in the tissues. Thirty characters (defined in Appendix 2) were measured using Fiji [@collins2007imagej;@schindelin2012fiji]. We did not measure the lengths of contractile structures (terminal filaments, pedicles, gastrozooids, and tentacles), since they are too variable to capture meaningful measurements. We measured at least one specimen for 96 different species (Appendix 3, Fig. \@(figure3)). Of these, we selected 38 focal siphonophore species based on specimen availability and phylogenetic representation from each clade. Three to five tentacle specimens from each one of these selected species were measured to capture intraspecific variation.

@@

  Phylogenetic logistic regressions identified evolutionary associations between individual characters and the presence of particular prey types in the diet (Fig. @\ref(figure5), right). Shifts toward ostracod presence in diet correlated with reductions in pedicle width and total haploneme volume. Shifts to copepod presence in the diet were associated with reductions in haploneme width, cnidoband length and width, total haploneme and heteroneme volumes, and tentacle and pedicle widths. Consistently, transitions to decapod presence in the diet correlated with more coiled cnidobands (Appendix 17).

@@

## Discussion {-}
  This core aims of this study are to examine the evolutionary history of siphonophore tentilla and diet, characterize the evolutionary shifts in their trophic niche, and identify the morphological characters that evolve with changes in prey type. We inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory, and whether the diets of siphonophores can be discriminated by observing their tentacles. In addition, we produced novel findings on tentilla morphology, siphonophore phylogeny, nematocyst character evolution, and tentillum discharge dynamics.

>>>>

^1^ Yale University, Department of Ecology and Evolutionary Biology, 165 Prospect St., New Haven, CT 06520, USA

@@

*Tentilla morphology* – The morphological work was carried out on siphonophore specimens fixed in 4% formalin from the Yale Peabody Museum Invertebrate Zoology (YPM-IZ) collection (catalog numbers in Appendix 1). These specimens had been collected intact across many years of fieldwork expeditions, by the means of blue-water Diving [@haddock2005scientific], remotely operated vehicles (ROVs), and human-operated submersibles. Tentacles were dissected from non-larval gastrozooids, sequentially dehydrated into 100% ethanol, cleared in methyl salicylate, and mounted into slides with Canada Balsam or Permount mounting media. The slides were imaged as tiled z-stacks using differential interference contrast (DIC) on an automated stage at YPM-IZ (with the assistance of Daniel Drew and Eric Lazo-Wasem) and laser point confocal microscopy using a 488 nm Argon laser that excited autofluorescence in the tissues. Thirty characters (defined in Appendix 2) were measured using Fiji [@collins2007imagej;@schindelin2012fiji]. We did not measure the lengths of contractile structures (terminal filaments, pedicles, gastrozooids, and tentacles), since they are too variable to capture meaningful measurements. We measured at least one specimen for 96 different species (Appendix 3, Fig. \@ref(figure3)). Of these, we selected 38 focal siphonophore species based on specimen availability and phylogenetic representation from each clade. Three to five tentacle specimens from each one of these selected species were measured to capture intraspecific variation.

@@

  Phylogenetic logistic regressions identified evolutionary associations between individual characters and the presence of particular prey types in the diet (Fig. \@ref(figure5), right). Shifts toward ostracod presence in diet correlated with reductions in pedicle width and total haploneme volume. Shifts to copepod presence in the diet were associated with reductions in haploneme width, cnidoband length and width, total haploneme and heteroneme volumes, and tentacle and pedicle widths. Consistently, transitions to decapod presence in the diet correlated with more coiled cnidobands (Appendix 17).

@@

## Discussion {-}
  The core aims of this study are to examine the evolutionary history of siphonophore tentilla and diet, characterize the evolutionary shifts in their trophic niche, and identify the morphological characters that evolve with changes in prey type. We inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory, and whether the diets of siphonophores can be discriminated by observing their tentacles. In addition, we produced novel findings on tentilla morphology, siphonophore phylogeny, nematocyst character evolution, and tentillum discharge dynamics.
